SVG: The Paper

### 2022-06-07 Analysis/index.Rmd
flipping y in hex plots

ggplot(d, aes(x, y)) + geom_hex(aes(colour = ..count..), bins = 12) +
  scale_fill_viridis_c() + scale_color_viridis_c() +
  my_theme -> plt_all

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y),
            .groups = "drop") %>%
  ggplot(aes(x, y)) + geom_hex(bins = 12) +
  scale_fill_viridis_c()+ scale_color_viridis_c() +
  my_theme -> plt_med

@@

>>>>

ggplot(d, aes(x, 1 - y)) + geom_hex(aes(colour = ..count..), bins = 12) +
  scale_fill_viridis_c() + scale_color_viridis_c() +
  my_theme -> plt_all

d %>% group_by(observer, condition) %>% 
  summarise(x = median(x), y = median(y),
            .groups = "drop") %>%
  ggplot(aes(x, 1 - y)) + geom_hex(bins = 12) +
  scale_fill_viridis_c()+ scale_color_viridis_c() +
  my_theme -> plt_med

@@

ggsave("../Figures/qjep_init_sel_preds.pdf", 
       plt1 / (plt2 + plt3)  + plot_layout(guides = "collect"),
       width = 10, height = 6)
